\section{Lecture 1: Graphs}

\subsection{Definitions}

\subsubsection*{Relation}
In a \textbf{relation}, the variable that you need to first is called the \textbf{independent variable}. Its 
value determine the value of the \textbf{dependent} variable. On the scatter plot, the independent variable 
in located on the \textbf{horizontal} axis and the dependent variable is located on the \textbf{vertical} axis.
The title of the graph should be \tit{dependent variable vs independent variable}

\subsubsection*{Scatter Plot}
A \textbf{scatter plot} is used to determine if a correlation exists between two \textbf{numerical} variables.
An \textbf{outlier} is a data point that does not fit the pattern of the other data. 

\subsubsection*{Line of best fit}
A \textbf{line of the best fit} can be used to model the data on a scatter plot whose points follow the trend of 
a line. A \textbf{curve} of best fit can be used to model the data on a scatter plot whose points follow the trend
of a curve. The line/curve should be solid if the data is \textbf{continuous} and dashed/dotted if the data is \textbf{discrete}

\subsubsection{Two variable graphed}
Using a scatter plot has a \textbf{positive} correlation if the trend of the data points increase from left to right. 
The two variables graphed using a scatter plot has a \textbf{negative} correlation if the trend of the data points
decrease from left to right. 

\subsubsection{Correlation}
The correlation between two variables is strong if the points on the scatter plot follow a line or a curve very closely. 
The correlation between two variables is \textbf{moderate} if the points on the scatter plot nearly follow a line or curve.
The correlation between two variables is \textbf{weak} if the points on the scatter plot are dispersed more widely, but 
still show a recognizable trend.\\

Two variables graphed on a scatter plot shows \textbf{no} correlation if the points are so scattered that no trend is 
discernible. 

\subsubsection*{Interpolate}
To \textbf{interpolate} means to estimate values lying between given data. To interpolate from a graph means to estimate
coordinates of points between those that are plotted. 

\subsubsection*{extrapolate}
To \textbf{extrapolate} means to estimate values lying outside the given range of data. To extrapolate 
from a graph means to estimate coordinates of points beyond those that are plotted. 

\subsubsection{Contingency}
A \textbf{contingency} table shows the frequency or percentage distribution of two categorical variables. 
