\section{Review of Describing and Graphing Motion}
\subsection{Position: $\vec{d}$}
Position is the \textbf{straight-line distance} from a fixed reference point to a location, together with the direction from the reference point to that location.

\subsection{displacement: $\Delta\vec{d}$}
Displacement is the \textbf{change in position}.\\
Formula:\\
\[
	\Delta\vec{d} = \vec{d_{2}} - \vec{d_{1}}
\] 
or \\
\begin{center}
    $n$ = the number of displacement vectors being added
\end{center}
\[
	\Delta\vec{d_{tot}} =  \sum_{i = 1}^{n} \Delta\vec{d_{i}}
\]

\subsection{Velocity: $\vec{v}$}
Velocity is the \textbf{rate of change of position}.
\[
	\vec{v} = \frac{\Delta\vec{d}}{\Delta t}
\]

\subsection{Acceleration: $\vec{a}$}
Acceleration is the \textit{rate of change} of velocity, and its units are always $\frac{m}{s^2}$.
\[
\vec{a} = \frac{\Delta \vec{v}}{\Delta t}
\]

\subsection{Graphing motion}
For a \textbf{position vs. time} graph:
\begin{itemize}
\item For a position or displacement vs. time graph, velocity is the \textit{slope}.
\item A slope of zero means the object is not moving.
\item Instantaneous velocity ($\vec{v}_{inst}$) is the slope of the \textbf{tangent} line to the graph at that instant.
\item Average velocity ($\vec{v}_{avg}$) is the slope of the \textbf{secant} line over that time interval.
\end{itemize}
For a \textbf{velocity vs. time} graph:
\begin{itemize}
    \item You can read an object's instantaneous velocity directly from the graph.
    \item Slope equals \textbf{acceleration}.
    \item Displacement is the \textbf{area} between the graph and the time axis over that interval.
\end{itemize}
