\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{ulem} % for \uline

\geometry{margin=1in}
\setstretch{1.2}

% A command to replace red text with blanks
\newcommand{\fillin}[1]{\uline{\hspace{#1}}}

\begin{document}

\section*{Space Race}
\subsubsection*{Cold War}
\begin{itemize}
    \item After World War II, two \fillin{4cm} emerged - the United States and the Soviet Union.
    \item Competition in \fillin{13cm}.
    \item The war was called "Cold" because there was no direct fighting
    \item US represents \fillin{10cm}.
    \item Soviet Union represents \fillin{4cm}
\end{itemize}

\subsubsection*{Nuclear Weapons (1949)}
\begin{itemize}
    \item Both side sought faster, safer delivery systems than aircraft - \newline leading to the need for \fillin{3cm}.
    \item Early research into \fillin{5cm} begins.
\end{itemize}

\subsubsection*{ICBMs (1950)}
\begin{itemize}
    \item ICBM stands for \fillin{8cm}.
    \item Both sides realized that the same technology could send \fillin{5cm} into orbits (such as satellites)
\end{itemize}

\subsubsection*{U.S ANNOUNCES SATELLITE PLAN (1955)}
\begin{itemize}
    \item (Eisenhower) announced plans to launch a \fillin{6cm} during the International Geophysical year (1957 ~ 1958), using ICBM technology.
    \item The project was led by the U.S Navy
\end{itemize}

\subsubsection*{SPUTNIK 1 (1957)}
\begin{itemize}
    \item Soviet launch \fillin{4cm}, A tiny \fillin{2cm} KG Satellie by R7 missile
    \item Its success \fillin{3cm} the western world and \fillin{3cm} ignited the space race
    \item Remainder: Soviet launch the satellite before US NAVY
\end{itemize}

\subsubsection*{Western's Reactions}
\begin{itemize}
    \item This news exploded like a nuclear bomb in Western \fillin{5cm}.
    \item Many people realized that the Soviet Union's technology was capable of \fillin{5cm} that the West had never \fillin{3cm}. 
\end{itemize}

\subsubsection*{US respond to the SPUTNIK 1(1958)}
\begin{itemize}
    \item The Soviet Union's achievements did not cause us any \fillin{3cm}; they simply sent a small ball into space.
    \item Finally, three month later, the United States sent an even \fillin{3cm} satellite to the space 
    \item In order to In order to counter the Soviet Union, President Eisenhower consolidated resources and established \fillin{3cm}.
\end{itemize}

\subsubsection*{\fillin{4cm}}
\begin{itemize}
    \item Aboard \fillin{3cm}, the first manned spacecraft
    \item Completed one \fillin{5cm} around Earth in 108 minutes
\end{itemize}

\subsubsection*{US respond to Gagain (1958)}
\begin{itemize}
    \item 23 days after Gagarin, \fillin{4cm} went to space by spacecraft Freedom 7
    \item \fillin{5cm}, reached 108 miles in altitude
    \item Soviet press downplayed it as a short "Up and Down" hop
\end{itemize}

\subsubsection*{Apollo Project (1962)}
\begin{itemize}
    \item Started after Kennedy's 1961 Moon goal
    \item Hired \fillin{4cm} peoples (36,000 NASA staffs and 375,000 contractors from companies such as Boeing and  Lockheed Martin)
\end{itemize}

\subsubsection*{Apollo 1 fire (1967)}
\begin{itemize}
    \item \fillin{5cm} caused the pure oxygen command module to \fillin{3cm}
    \item \fillin{5cm} killed - safety overhaul
\end{itemize}

\subsubsection*{The road to the moon (1968 - 1969)}
\begin{itemize}
    \item Apollo \fillin{1cm}: First crew to orbit the moon (Dec 1968)
    \item Apollo \fillin{1cm}: tests Lunar Module in Earth Orbit (Mar 1969)
    \item Apollo \fillin{1cm}: full "Dress rehearsal" (May 1969)
\end{itemize}

\subsubsection*{Apollo 11}
\begin{itemize}
    \item July 20 1969: \fillin{8cm} landed on the moon
    \item Soviet: never \fillin{3cm} to compete with the United States in landing on the moon
\end{itemize}

\newpage
\subsection*{Student activity / practice for the test}
\subsubsection*{instruction}
\begin{itemize}
    \item Using your notes to fill in the blanks in the sentences
    \item Then, arrange it by timeline.
\end{itemize}

\begin{enumerate}[label=\textbf{\Alph*.}]
    \item The first \textbf{human spaceflight} --- \fillin{5cm} aboard \textit{Vostok 1}.
    \item The \textbf{United States} established \fillin{3cm} to organize its space program.
    \item Apollo\fillin{1cm} became the first crewed mission to \textbf{orbit the Moon}.
    \item The \textbf{Soviet Union} successfully tested its first \textbf{atomic bomb} (\textit{RDS-1}).
    \item \fillin{6cm} became the first \textbf{American in space} aboard \textit{Freedom 7}.
    \item Both US and USSR started to develop ICBMs
    \item President \textbf{Kennedy} announceed the goal to \fillin{7cm} before 1970.
    \item The \textbf{Soviet Union} launched \fillin{5cm}, the first \textbf{artificial satellite}.
    \item The \textbf{United States} publicly announceed a plan to \fillin{9cm} during the International Geophysical Year.
    \item Apollo\fillin{1cm} astronauts \textbf{landed on the Moon}, achieving Kennedy’s goal.
\end{enumerate}

Write your answers here:\\

Example. 1. 1945 K - Event k happened in 1945 and be the first in the timeline \\

1. 1949 \fillin{3cm}\\

2. 1950 \fillin{3cm}\\

3. 1955 \fillin{3cm}\\

4. 1957 \fillin{3cm}\\

5. 1958 \fillin{3cm}\\

6. 1961 \fillin{3cm}\\

7. 1961 \fillin{3cm}\\

8. 1961 \fillin{3cm}\\

9. 1968 \fillin{3cm}\\

10. 1969 \fillin{3cm}\\

\end{document}
