\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{ulem} % for \uline

\geometry{margin=1in}
\setstretch{1.2}

% A command to replace red text with blanks
\newcommand{\fillin}[1]{\uline{\hspace{#1}}}

\begin{document}

\section*{History of Space Science to 1700s}

\subsection*{Myths}
At the beginning of mankind, early civilizations did not understand modern science. 
They created \fillin{6cm} to explain the universe.

\paragraph{Example I: Pangu Creates the World}
\begin{enumerate}
  \item From \fillin{6cm}.
  \item Pangu used his \textbf{hands and legs} to break the chaos.
  \item His \fillin{2cm} eye became the Sun.
  \item His \fillin{2cm} eye became the Moon.
  \item His \fillin{2cm} became the soil.
\end{enumerate}

\paragraph{Example II: The Turtle Island Myth}
\begin{itemize}
  \item From \fillin{8cm}.
  \item The Earth was formed on the back of a giant \fillin{2.5cm} -- ``Turtle Island''.
  \item A woman gave birth to twins.
  \item The \fillin{3cm} Twin placed the Sun in the sky for \fillin{5cm}.
  \item The \fillin{3cm} Twin placed the Moon in the sky for \fillin{5cm}.
  \item Such myths explained the \fillin{4cm} before scientific astronomy.
\end{itemize}

\subsection*{Ancient Greek Astronomy}
\paragraph{Eudoxus (390–337 BCE)}
\begin{itemize}
  \item Proposed the first geometric model of planetary motion.
  \item Used \fillin{2cm} concentric spheres with Earth at the center.
  \item First to use \fillin{3cm} and \fillin{3cm} to analyze the heavens (universe).
\end{itemize}

\paragraph{Aristotle (384–322 BCE)}
\begin{itemize}
  \item Expanded \fillin{5cm} using about \fillin{2cm} concentric spheres.
  \item Earth is a \fillin{2cm} and \fillin{2.5cm} at the universe's center.
  \item Everything travels in \fillin{8cm}.
  \item The universe is \fillin{5cm} and finite.
\end{itemize}

\paragraph{Ptolemy (100–170 AD)}
\begin{itemize}
  \item Developed the \fillin{5cm} model.
  \item Introduced \fillin{5cm} to explain \fillin{5cm}.
\end{itemize}

\subsection*{Heliocentric System}
\paragraph{Copernicus}
\begin{itemize}
  \item Proposed the \fillin{5cm} universe.
  \item Planets arranged by \fillin{8cm}.
  \item \fillin{3cm} explained by Earth’s motion, no epicycles needed.
\end{itemize}

\paragraph{Tycho Brahe}
\begin{itemize}
  \item Built \fillin{3cm}.
  \item Proposed a \fillin{3cm} model.
\end{itemize}

\paragraph{Johannes Kepler}
\begin{itemize}
  \item Showed planetary orbits are \fillin{2.5cm}.
  \item Laws of Planetary Motion: \fillin{5cm}.
\end{itemize}

\paragraph{Galileo Galilei}
\begin{itemize}
  \item First to use a \fillin{3cm} for astronomy.
  \item Discovered moons of \fillin{3cm}.
  \item Opposed the \fillin{3cm} model.
  \item Condemned by the \fillin{4cm}.
\end{itemize}

\subsection*{Practice Activity}
\begin{enumerate}
    \item Use the word bank to fill in the blank names in each sentence.
    \item After filling in all names, arrange the scientists in \textbf{chronological order} on your own timeline.
\end{enumerate}

\subsection*{Word Bank}
Eudoxus, Aristotle, Ptolemy, Copernicus, Tycho Brahe, Kepler, Galileo Galilei

\subsection*{Sentences}
\begin{enumerate}
    \item \fillin{3cm} developed \textbf{concentric spheres} to explain planetary motion.
    \item \fillin{3cm} used a \textbf{telescope} to observe moons of Jupiter, phases of Venus, and supported heliocentrism publicly.
    \item \fillin{3cm} proposed a \textbf{Sun-centered (heliocentric) universe} with circular orbits, still keeping some small epicycles.
    \item \fillin{3cm} wrote the \textbf{Almagest} and introduced \textbf{epicycles} to explain \textbf{retrograde motion}.
    \item \fillin{3cm} formulated \textbf{Kepler's laws of planetary motion}: elliptical orbits, equal areas in equal times, period-distance law.
    \item \fillin{3cm} built precise observatories and collected extremely accurate astronomical data.
    \item \fillin{3cm} proposed a \textbf{geocentric model} with a \textbf{spherical Earth} and \textbf{perfect circular orbits}.
\end{enumerate}

\section*{Optional}
Draw a simple horizontal timeline and place each number in chronological order.

\subsection*{Please write your answer here:}
1. \fillin{3cm}  
2. \fillin{3cm}  
3. \fillin{3cm}  
4. \fillin{3cm}  
5. \fillin{3cm}  
6. \fillin{3cm}  
7. \fillin{3cm}

\end{document}
