\chapter{Testible questions}
\section{Formation of the solar system}
\subsection{Question 1}
According to the Nice Model, what caused the "reorganization of the solar system?"
\begin{itemize}
    \item Jupiter's and Saturn's 2:1 orbital resonance. 
\end{itemize}

\subsection{Question 2}
Summary the Nebular Theory:
\begin{itemize}
    \item Collapse of a nebular due to gravity
    \item Majority of the material from the clouded ended up in the center - forming the early Sun 
    \item The shrinking and accelerating caused the cloud to flatten into a protoplanetary disk. 
    \item The disk was the birth place of the planet
\end{itemize}

\subsection{Question 3}
Match the letters or dates to their correct imper period of events
\subsubsection{4.6 billion years ago}
The Birth of our solar system

\subsubsection{4.59 billion years ago}
\begin{itemize}
    \item Jupiter and Saturn's migration towards the sun
    \item Formation of outer planet
\end{itemize}

\subsubsection*{4.5 billion years ago}
\begin{itemize}
    \item Earth, Venus, Mars and Mercury are formed
    \item Proto-Earth's collision with "Theia", leading to the formation of our Moon
\end{itemize}

\subsubsection*{4.48 billion years ago}
\begin{itemize}
    \item The outward migration of the outer planet
    \item The Kuiper Belt is formed
\end{itemize}

\subsubsection{4.1 to 3.8 billion years ago}
\begin{itemize}
    \item The late Heavy Bombardment (Large-scale asteroid and comet impact events)
\end{itemize}

\section{The Moon}
\subsection{Question 1}
Explain two ways the Moon's surface preserves historical evidence better than the Earth's surface:
\begin{itemize}
    \item Lack an atmosphere, so no weathering or erosion occurs
    \item Has no tectonic activity - which would recycle surface materials. 
\end{itemize}

\subsection{Question 2}
Why the discovery of water ice on the Moon could support future exploration. 
\begin{itemize}
    \item Provide drinking water
    \item Split into hydrogen and oxygen, using hydrogen for rocket fuel and the oxygen for human respiration
\end{itemize}

\section{The space race}
\subsection{Question 1}:
The intercontinental ballistic missiles designed for nuclear weapons

\subsection{Question 2}
It challenged the US. claims of technological superiority\\

It starts a psychological and politcal crisis, leading to the creation of NASA

\section{Other objects in our solar system}
\subsection{Question 1}
Two required characteristics of a planet is that it orbits the Sun and must have enough mass so that it is a mostly spherical shape? 
What is the third characteristic?
\begin{itemize}
    \item The planet must be big enough for its gravity to clear the way of other objects
\end{itemize}

\subsection{Question 2}
\begin{itemize}
    \item (Meteoroid): A small body moving in the solar system
    \item (Meteor): The streak of light that appears when a meteoroid passes thourht Earth's atmosphere
    \item (Meteorite): The portion f a meteorid that hits the ground. 
\end{itemize}

\section{Tech used to study the properties of the planets in our solar system}
\subsection{Question 1}
How do magnetometers work?
\begin{itemize}
    \item Similar to a fine turned compass
\end{itemize}

\subsection{Question 2}
Explain one important reason why scientists care about measuring a planets' properties?
\begin{itemize}
    \item Help us to identify the gaps in astrophysics that we do not know yet
\end{itemize}

\subsection{Question 3}
The differences between \textbf{spectroscope} and a \textbf{spectrometer}?
\begin{itemize}
    \item (Spectroscope): is an instrument that separates light into its wavelength to from a spectrum
    \item (Spectrometer): is a specialized spectroscope that takes samples of a spectrum to study different components
\end{itemize}

\subsection{Question 4}
Explain one method or instrument used to measure the mass of a planet?
\begin{itemize}
    \item Use telescopes to observe gravitational influence
\end{itemize}

\section{Rockets}
\subsection{Question 1}
4 major systems of a rocket:
\begin{itemize}
    \item Structural, guidance, payload, propulsion
\end{itemize}

\subsection{Question 2}
What are the two factors that determine whether something is a rocket?
\begin{itemize}
    \item Carries its own fuel and oxidizer
    \item Eject material out for thrust
\end{itemize}

\subsection{Question 3}:
Purpose of orbital launch vehicles:
\begin{itemize}
    \item Fireworks: Rockets are used to launch fireworks to a safe altitude. 
    \item Atomospheric Research: Rockets are used to transport data collection equipment to areas of our atmosphere that neither weather ballons nor 
    satellites can reach
\end{itemize}

\section{The Canadarm}
\subsection{Question 1}
Three joints of Canadarm
\begin{itemize}
    \item Shoulder
    \item Elbow
    \item Wrist
\end{itemize}

\subsection{Question 2}
Characterists of Canadarm: 
\begin{itemize}
    \item (Controlled by): Autonomously by AI, people in Canada, or astronauts on Gateway
    \item (Base): Move from End to End on Gateway
    \item (Degree of Freedom): 7
\end{itemize}

\section{The militarization of space}
\subsection{Question 1}
Why is the weaponization of space difficult to regulate under the 1967 Outer space treaty?
\begin{itemize}
    \item Because it bans only nuclear weapon in space
\end{itemize}

\subsection{Q2}
Why are anti-satellite weapons considered a global risk?
\begin{itemize}
    \item Destroying a satellite creates debris that can collide with other satellite. 
    \item This may cause a chain reaction
    \item The could put the ISS and important civilian satellites at risk
\end{itemize}

\section{Space debris}
\subsection{Q1}
Kessler Syndrome?
\begin{itemize}
    \item A chain reaction which collisions of space debris creates even more debris over time
\end{itemize}

\subsection{Q2}
One strategy for reducing space debris\\

Laser:
\begin{itemize}
    \item Lasers are used to push smal pieces of debris and change their orbits
    \item Works by slightly heating one side of them
\end{itemize}

\section{Planned development on the Moon}
\subsection{Q1}
Artemis:
\begin{itemize}
    \item To establish a long-term human presence on the Moon
\end{itemize}

\subsection{Q2}
Outer Space Treaty states:
\begin{itemize}
    \item No country owns the Moon
    \item Military bases on celestial bodies are prohibited
\end{itemize}

\section{Potential human missions to Mars}
\subsection{Q1}
Why was Mars chosen as a potential future habitat for humans beyond Earth?
\begin{itemize}
    \item It has usable resources like frozen watern and is the most like Earth
\end{itemize}

\subsection{Q2}
Describe the risk of cosmic rays on Mars?
\begin{itemize}
    \item Excessive exposure to radiation
    \item This can cause health problems
\end{itemize}

\section{Biology and Psychology long space mission}
\subsection{Q1}
During the first few days in microgravity, astronauts experience motion sickness and fluid shifting towards the upper body. What is this condition called?
\begin{itemize}
    \item Space Adapitation Syndrome
\end{itemize}

\subsection{Q2}
What is the primary cause of bone loss experienced by astronauts during long-duration space missions?
\begin{itemize}
    \item The "weightless" environment reduces the mechanical load on bones
\end{itemize}

\subsection{Q3}
Two important pyschological challenges that astronauts experience during long space mission
\begin{itemize}
    \item Isolation
    \item Homesick
\end{itemize}

\subsection{Q4}
Circle one of your answers above and for that challenge explain one countermeasure that helps astronauts manage it. (1 mark)
\begin{itemize}
    \item Isolation \& Homesick: Communication with families and friends on Earth
\end{itemize}

\section{Why have aliens not visited us yet?}
\subsection{Q1}
Describe two reasons why technology may be a limiting factor when it comes to communicating with extraterrestrial life.
\begin{itemize}
    \item there are too far away to contact with our current technology
    \item Extraterrestrials may use a form of communication that we cannot detect
\end{itemize}

\subsection{Fermi Paradox}
There is a discrepancy between:
\begin{itemize}
    \item the lack of conclusive evidence of advanced extraterrestrial life, and 
    \item the high probability of existence. 
\end{itemize}